Visualizations for the manuscript

### 2022-04-04 metanalysis_visualization/manuscript_Figures.Rmd
fixing subgroup percentages count

```{r}

perc_disorder_group_total_fix <- perc_disorder_group_all %>%
  group_by( time_p, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             percentage = mean(percentage_dg * count_icd / total_diagnoses, na.rm = TRUE), 
             country = "ALL")

>>>>

```{r}
table_iterations_disorder <- with(perc_disorder_group_all,
  expand.grid(time_p = unique(time_p),
              disorder_group = unique(disorder_group), 
              siteid = unique(siteid)
  )
)

perc_disorder_group_complete <- perc_disorder_group_all %>% 
  full_join(table_iterations_disorder) %>% 
  arrange(siteid, time_p, disorder_group) %>% 
  group_by(siteid, time_p) %>% 
  fill(count_icd, 
       period, 
       country , 
       plotsLabel, 
       .direction = "downup") %>% 
  ungroup() %>% 
  replace_na(list(count_dg = 0, percentage_dg = 0))

perc_disorder_group_total_fix <- perc_disorder_group_complete %>%
  group_by( time_p, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             sum_dg_psy = sum(count_dg),
             percentage = (sum_dg_psy / total_diagnoses) * 100, 
             country = "ALL")
